### 2021-09-06 input/proposal.tex
about proof

To assign and maintain \processes to their best partition according to
replica creations and removals, as well as dynamic infrastructure
changes, we designed and implemented \NAME.  \NAME stands for
\underline{A}daptive \underline{S}coped broad\underline{cast}. It
relies on a primitive that allows a \process to broadcast a message
within a limited scope. We first use this primitive to guarantee
consistent partitioning when a \process can only create a new replica
within the system. We highlight the issue when a process can also
destroy a replica, and provide a second algorithm that handles replica
removals as well as dynamic changes of the infrastructure.  This
section describes the communication primitive called scoped broadcast,
then discusses the properties that guarantee consistent partitioning
in our context, and finally details our implementation \NAME and the
analysis of its complexity.

@@

\begin{definition}[\label{def:lwo}Message staleness]
  A message $m$ conveys \underline{s}tale control information if the
  process that broadcast $m$ later broadcast another message $m'$:
  $S(m) = \exists m': b_p(m) \rightarrow b_p(m')$.

@@

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming BEF as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [BEF without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
    consistent partitioning.
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by BEF:]
    %% also transiting messages
    Assuming that every process removes control information as soon as
    they become stale ($S(\alpha_a^x) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m_1) \rightarrow \ldots
    \rightarrow d_c(m_k \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, the \process never
    ends up in its best partition. Therefore, \processes do not reach
    consistent partitioning.
  \item [Purge then BEF:] Assuming the eventual removal of stale
    control information ,

    nothing stops up-to-date control information to propagate, as in
    Theorem~\ref{theo:bef}. Assuming that removal of stale control
    information immediatly triggers a forwarding of best up-to-date
    %% Removing \emph{forever} all such stale messages about
    %% deleted partitions would allow \processes to propagate their best
    %% up-to-date partition again, eventually reaching consistent
    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
  \end{asparadesc}
\end{proof}

@@

@@

\begin{figure}
  \centering\input{input/figproofB.tex}
  \caption{\label{fig:proofB}Stale $\alpha$ messages may
      stop $\delta$ messages from reaching processes with the corresponding
      partition. Consistent partitioning requires that all \processes propagate
      $\delta$ messages as often as possible (I'); detect possible inconsistencies
      when parents' $\alpha$ messages contradict history or state (III); notify
      processes of possible inconsistencies (IV)}
\end{figure}

@@

>>>>

To assign and maintain \processes to their best partition according to
replica creations and removals, as well as dynamic infrastructure
changes, we designed and implemented \NAME.  \NAME stands for
\underline{A}daptive \underline{S}coped broad\underline{cast}. It
relies on a primitive that allows a \process to broadcast a message
within a limited scope. We first use this primitive to guarantee
consistent partitioning when a \process can only create a new replica
within the system. We highlight the issue when a \process can also
destroy a replica, and provide a second algorithm that handles replica
removals as well as dynamic changes of the infrastructure.  This
section describes the communication primitive called scoped broadcast,
then discusses the properties that guarantee consistent partitioning
in our context, and finally details our implementation \NAME and the
analysis of its complexity.

@@

\begin{definition}[\label{def:lwo}Message staleness]
  A message $m$ conveys \underline{s}tale control information if the
  \process that broadcast $m$ later broadcast another message $m'$:
  $S(m) = \exists m': b_p(m) \rightarrow b_p(m')$.

@@

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming BEF as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [BEF without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
    consistent partitioning.
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by BEF:]
    %% also transiting messages
    Assuming that every \process removes control information as soon as
    it becomes stale ($S(\alpha_a^x) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m_1) \rightarrow \ldots
    \rightarrow d_c(m_k \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, the \process never
    ends up in its best partition. Therefore, \processes do not reach
    consistent partitioning.
  \item [Purge then BEF:] Assuming the eventual and definitive removal
    of stale messages at each \process, eventually every process only
    delivers and forwards up-to-date messages, or no message at
    all. Assuming that eventually, each removal triggers the
    forwarding of best delivered messages, every \processes eventually
    delivers and forwards the best up-to-date delivered
    messages. \Processes reach consistent partitioning together.
    %% Removing \emph{forever} all such stale messages about
    %% deleted partitions would allow \processes to propagate their best
    %% up-to-date partition again, eventually reaching consistent
    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
  \end{asparadesc}
\end{proof}

@@

\TODO{The challenge is therefore about purging.}

@@

@@

\begin{figure}
  \centering\input{input/figproofB.tex}
  \caption{\label{fig:proofB}Stale $\alpha$ messages may
      stop $\delta$ messages from reaching \processes with the corresponding
      partition. Consistent partitioning requires that all \processes propagate
      $\delta$ messages as often as possible (I'); detect possible inconsistencies
      when parents' $\alpha$ messages contradict history or state (III); notify
      \processes of possible inconsistencies (IV)}
\end{figure}
